---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

EX 27.2.1

1. Created Notebook (current file)

2. Created Markdown Document and program asked me to enter the title and author and then automatically added it to the header for me.

3. I'm not noticing anythig different? I switched YAML and barely noticed a change.

4. I enjoyed the different knit options. HTML outputs what looks like a webpage, where the Word outputs directly into Word (seems very useful), PDF formats directly to PDf

EX 27.2


```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)

smaller <- diamonds %>% 
  filter(carat <= 2.5)
```

We have data about `r nrow(diamonds)` diamonds. Only 
`r nrow(diamonds) - nrow(smaller)` are larger than
2.5 carats. The distribution of the remainder is shown
below:

```{r, echo = FALSE}
smaller %>% 
  ggplot(aes(carat)) + 
  geom_freqpoly(binwidth = 0.01)
```


EX 27.3 see Markdown file



